\documentclass[10pt]{amsart}

\usepackage{macros,amsmath}

%Formatting
\linespread{1.25}

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{5}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\title{Response to referee report}

\author{Brian R. Williams}
\address{Northeastern University}
\email{brwilliams@northeastern.edu}
\urladdr{}

\date{}

\begin{document}

\maketitle

\begin{itemize}
\item[(1)] Fixed.
\item[(2)] Fixed.
\item[(3)] \brian{to do}
\item[(4)] Fixed.
\item[(5)] Added ``Notation" section at the end of introduction. 
\item[(6)] Fixed.
\item[(7)] Fixed, throughout paper. 
\item[(8)] Fixed.
\item[(9)] Have reformulated the presentation of the BV pairing. 
It is summarized in Lemma 2.18 now.
\item[(10)] Added paragraph in the beginning of Section 2.2. 
\item[(11)] Fixed.
\item[(12)] Fixed.
\item[(13)] Fixed.
\item[(14)] Fixed.
\item[(15-16)] In the definition of invariants for $\CC^{2d|d}$ the terms involving $\frac{\partial}{\partial \zbar_i}$ and $\Bar{\eta}_i$ are allowed. 
I've defined a new complex $\sO_{\rm loc}^{hol,trans}$ for which only derivatives $\frac{\partial}{\partial z_i}$ are allowed.
Lemma 2.30 shows these two complexes are equivalent. 
\item[(17)] The example is incorrect. I've added a new example. 
\item[(18)] I've added Definition 2.19. 
\item[(19)] Fixed.
\item[(20)] Fixed.
\item[(21)] I've extended the remark to clarify. 
\item[(22)]Fixed.
\item[(23)] \brian{Pull from desktop}. 
\item[(24)] Fixed.
\item[(25)] Here are the changes I have made:
\begin{itemize}
\item I have added a remark under the statement of Lemma 3.11 citing the reference by Kevin Costello, Si Li "Quantization of open-closed BCOV theory, I". 
\item I have added a paragraph before Lemma 3.12 citing the reference Kevin Costello, Si Li: ``Quantization of open-closed BCOV theory, I".
\item I have added a reference to Si Li: ``Feynman graph integrals and almost modular forms" in the definition of the operators $D_{\alpha,i_\alpha}$ in the proof of Lemma 3.12 and Lemma 3.13. 
\item Added a paragraph citing Si Li and Qin Li: "On the B-twisted topological sigma-model and Calabi-Yau geometry" before Lemma 4.3. 
\item Added a remark after Proposition 4.4. 

\end{itemize}



\end{itemize}


\end{document}
